General Procedure

### 2018-07-17 statement.tex
Timo stinkt viel mehr!!!!

\section{Timo}	
My main focus at the start of the practicum was to create a sophisticated generator for different testsets, with the sizes and properties like different sizes and distribution, for which I wrote the \texttt{testDataGenerator.py}. All this includes an analysis of the data with the whole team. Further, I implemented the vector computation of mapping movements to persons and computing the vector format proposed by Miriam. All those different options are choose-able through commandline flags. For the whole script I wrote comments and documentation in order to provide a reusable base.\\
Later through the project my focus was to aid during various tasks. Therefore, Martin and me build different neural net architectures and tested them under various conditions and wrote the results down for the final paper.\\
Also Miriam and I tried several different clusterings, which she build in RapidMiner. We also prepared and practiced the presentation, which included the tasks of thinking about topics, which were not included of the technical part of our team. Like, a precise but short introduction or reasons for the problem, that we cannot reproduce or find clusters, we faced.\\
After the presentation we merged the different written parts of our team members and made additions or replacements if necessary. After the feedback from María, also Miriam and I, restructured and basically (re-)wrote certain aspects. This 
was finished by proofreading and fine tuning through the two of us.
\end{document}

>>>>

\section{Timo}	
%#Streber
%#PizzaFresser
%#WohntMitFranzosenZusammen
%#Sonnenbrand
My main focus at the start of the practicum was to create a sophisticated generator for different testsets, with the sizes and properties like different sizes and distribution, for which I wrote the \texttt{testDataGenerator.py}. All this includes an analysis of the data with the whole team. Further, I implemented the vector computation of mapping movements to persons and computing the vector format proposed by Miriam. All those different options are choose-able through commandline flags. For the whole script I wrote comments and documentation in order to provide a reusable base.\\
Later through the project my focus was to aid during various tasks. Therefore, Martin and me build different neural net architectures and tested them under various conditions and wrote the results down for the final paper.\\
Also Miriam and I tried several different clusterings, which she build in RapidMiner. We also prepared and practiced the presentation, which included the tasks of thinking about topics, which were not included of the technical part of our team. Like, a precise but short introduction or reasons for the problem, that we cannot reproduce or find clusters, we faced.\\
After the presentation we merged the different written parts of our team members and made additions or replacements if necessary. After the feedback from María, also Miriam and I, restructured and basically (re-)wrote certain aspects. This 
was finished by proofreading and fine tuning through the two of us.
\end{document}
